A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-10 paper/prab.tex
copied paper into prab template

\documentclass[final]{siamltex}

\usepackage{todonotes}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{url}
\usepackage{footmisc}
\usepackage{multicol}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,snakes,backgrounds}
\usetikzlibrary{mindmap,trees}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{plotmarks}
\usepackage{subcaption}

\usepackage{listings}
\newcounter{lstmain}
\setcounter{lstmain}{1}

@@

\newcommand{\nrnote}[1]{\textsf{{\color{violet}{ NN note:}   #1 }}}
\begin{document}

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Beam Dynamics}

\author{N. Neveu\footnotemark[7]\ \footnotemark[8]
  \and Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
  \and P. Arbenz\footnotemark[4]
  \and C. Bekas\footnotemark[3]
  \and A. Curioni\footnotemark[3]
  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
  \and C. Metzger-Kraus 
}

\maketitle

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[2]{PSI, Villigen, Switzerland}
\footnotetext[3]{IBM Research -- Zurich, Switzerland}
\footnotetext[4]{Department of Computer Science, ETH Zurich, Switzerland}
\footnotetext[5]{University of Huddersfield, West Yorkshire, United Kingdom}
\footnotetext[1]{Illinois Institute of Technology, Chicago, USA}
\footnotetext[8]{Argonne National Laboratory, Lemont, USA}
\footnotetext[6]{Corresponding author: \url{andreas.adelmann@psi.ch}}
\renewcommand{\thefootnote}{\arabic{footnote}}

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.

We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame we require a fast
  and scalable software framework.

In this paper, we present the implementation of such a general-purpose
  framework for simulation-based multi-objective optimization methods that
  allows the automatic investigation of optimal sets of machine parameters.
The implementation is based on a master/slave paradigm, employing several
  masters that govern a set of slaves executing simulations and performing
  optimization tasks.

Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
  forward solver in our framework, we present validation experiments and first
  results of multi-objective optimization problems in the domain of beam
  dynamics.
\end{abstract}

\begin{keywords}
multi-objective optimization, beam dynamics, high performance computing
\end{keywords}

@@

\begin{figure}[h!]
\begin{center}\normalsize

	\pgfdeclarelayer{background}
	\pgfsetlayers{background,main}
  \begin{tikzpicture}[text=black]%[scale=0.95, transform shape]
    \input{figures/opt-framework_code.tex}
  \end{tikzpicture}
\caption{Multi-objective framework: the pilot (master) solves the
optimization problem specified in the input file by coordinating optimizer
algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{center}
\end{figure}

@@

To allow arbitrary constraints and objective expressions, such as
%
\vspace{0.2cm}
{\footnotesize \begin{verbatim}
  name: OBJECTIVE,
        EXPR="5 * average(42.0, "measurement.dat") + ENERGY";
\end{verbatim}}
\vspace{0.2cm}
%
\noindent
  we implemented an expression parser using Boost
  Spirit\footnote{\url{http://boost-spirit.com/}}.
In addition to the parser, we need an evaluator able to evaluate an expression,
  given a parse tree and variable assignments to an actual value.
Expressions arising in multi-objective optimization problems usually evaluate
  to booleans or floating point values.
The parse tree, also denoted abstract syntax tree (AST), is constructed
  recursively while an expression is parsed.
Upon evaluation, all unknown variables are replaced with values, either
  obtained from simulation results or provided by other subtrees in the AST.
In this stage, the AST can be evaluated bottom-up and the desired result is
  returned after processing the root of the tree.

To improve the expressive power of objectives and constraints we introduced a
  simple mechanism to define and call custom functions in expressions.
Using simple functors, e.g., as the one shown in Listing 4 to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost
  variants\footnote{\url{www.boost.org/doc/html/variant.html}} that can be
  booleans, strings or floating point values.

@@

All custom functions are registered with expression objects.
This is necessary to ensure that expressions know how they can resolve
  function calls in their AST.
As shown in Listing 5 this is done by creating a collection of Boost
  functions\footnote{\url{www.boost.org/libs/function/}} corresponding to the
  available custom functions in expressions and passing this to the
  \textsc{Pilot}.

>>>>

\documentclass[%
reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{booktabs}
%\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{url}
%\usepackage{footmisc}
%\usepackage{multicol}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,snakes,backgrounds}
\usetikzlibrary{mindmap,trees}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{plotmarks}
\usepackage{listings}
\newcounter{lstmain}
\setcounter{lstmain}{1}

@@

\newcommand{\nrnote}[1]{\textsf{{\color{violet}{ NN note:}   #1 }}}

\begin{document}

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Beam Dynamics}
%\thanks{A footnote to the article title}%

\author{N. Neveu}
\altaffiliation[Also at ]{Argonne National Laboratory, USA}%Lines break automatically or can be forced with \\

\author{L. Spentzouris}
\affiliation{Illinois Institute of Technology, Chicago, IL}

\author{Andreas Adelmann}
\email{andreas.adelmann@psi.ch}
\author{A. Kolano}
\altaffiliation[Also at ]{
	University of Huddersfield, West Yorkshire, United Kingdom}

\affiliation{
	PSI, Villigen, Switzerland}%

\author{Y Ineichen}%
\altaffiliation[Also at ]{Department of Computer Science, ETH Zurich, Switzerland}%Lines break

\author{C. Bekas}
\author{A. Curioni}

\affiliation{IBM Research, Zurich, Switzerland }%

\author{P. Arbenz}
\affiliation{%
	Department of Computer Science, ETH Zurich, Switzerland}%

\author{C. Metzger-Kraus }
\affiliation{% 
	place holder \\
}%

\date{\today}% It is always \today, today,
%  but any date may be explicitly specified

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame we require a fast
  and scalable software framework.
In this paper, we present the implementation of such a general-purpose
  framework for simulation-based multi-objective optimization methods that
  allows the automatic investigation of optimal sets of machine parameters.
The implementation is based on a master/slave paradigm, employing several
  masters that govern a set of slaves executing simulations and performing
  optimization tasks.
Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
  forward solver in our framework, we present validation experiments and first
  results of multi-objective optimization problems in the domain of beam
  dynamics.

\end{abstract}

\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
% Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
%display desired
\maketitle

@@

\begin{figure}%[h!]
%\begin{center}\normalsize
	\scalebox{0.8}{
	\pgfdeclarelayer{background}
	\pgfsetlayers{background,main}
	\begin{tikzpicture}[text=black]%[scale=0.05]%, transform shape]
	\input{figures/opt-framework_code.tex}
	\end{tikzpicture}
}
%\end{center}
%\end{center}
\caption{Multi-objective framework: the pilot (master) solves the
	optimization problem specified in the input file by coordinating optimizer
	algorithms and workers running forward solves.}
\end{figure}\label{fig:framenetwork}

@@

To allow arbitrary constraints and objective expressions, such as
%
\vspace{0.2cm}
{\footnotesize \begin{verbatim}
  name: OBJECTIVE,
        EXPR="5 * average(42.0, "measurement.dat") + ENERGY";
\end{verbatim}}
\vspace{0.2cm}
%
\noindent
  we implemented an expression parser using Boost
%  Spirit\footnote{\url{http://boost-spirit.com/}}.
In addition to the parser, we need an evaluator able to evaluate an expression,
  given a parse tree and variable assignments to an actual value.
Expressions arising in multi-objective optimization problems usually evaluate
  to booleans or floating point values.
The parse tree, also denoted abstract syntax tree (AST), is constructed
  recursively while an expression is parsed.
Upon evaluation, all unknown variables are replaced with values, either
  obtained from simulation results or provided by other subtrees in the AST.
In this stage, the AST can be evaluated bottom-up and the desired result is
  returned after processing the root of the tree.

To improve the expressive power of objectives and constraints we introduced a
  simple mechanism to define and call custom functions in expressions.
Using simple functors, e.g., as the one shown in Listing 4 to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost
%  variants\footnote{\url{www.boost.org/doc/html/variant.html}} that can be
  booleans, strings or floating point values.

@@

All custom functions are registered with expression objects.
This is necessary to ensure that expressions know how they can resolve
  function calls in their AST.
As shown in Listing 5 this is done by creating a collection of Boost
%  functions\footnote{\url{www.boost.org/libs/function/}} corresponding to the
  available custom functions in expressions and passing this to the
  \textsc{Pilot}.
